3D Magnetic modelling of ellipsoidal bodies

### 2017-02-14 manuscript/manuscript.tex
orientation angles strike, dip and rake

Let $(x, y, z)$ be a point referred to a Cartesian coordinate system with axes
$x$, $y$ and $z$ pointing to, respectively, North, East and down.
For convenience, we denominate this coordinate system as 
\textit{main coordinate system}.
Let us consider an ellipsoidal body with centre at the point $(x_{c}, y_{c}, z_{c})$,
semi-axes defined by positive constants $a$, $b$, $c$, 
where $a > b > c$, and orientation defined by
three angles $\alpha$, $\beta$, and $\gamma$.

DESCREVER A ORIENTACAO EM FUNCAO DOS ANGULOS DE GEOLOGIA ESTRUTURAL
\citep{clark1986, allmendinger2012}

@@

Figure \ref{fig:fig1} TEXT TEXT TEXT Fig. \ref{fig:fig1} TEXT TEXT TEXT (Fig. \ref{fig:fig1})

@@

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/demag_factors.pdf}
\caption{TEXT}
\label{fig:fig1}
\end{figure}

>>>>

Let $(x, y, z)$ be a point referred to a Cartesian coordinate system with axes
$x$, $y$ and $z$ pointing to, respectively, North, East and down.
For convenience, we denominate this coordinate system as 
\textit{main coordinate system} (Fig. \ref{fig:orientation-angles}a).
Let us consider an ellipsoidal body with centre at the point $(x_{c}, y_{c}, z_{c})$,
orientation defined by angles \textit{strike}, \textit{dip}, and
\textit{rake} (Fig. \ref{fig:orientation-angles}a), and semi-axes defined by
positive constants $a$, $b$, $c$ (Fig. \ref{fig:orientation-angles}b).
The angles strike, dip and rake are commonly used to
define the orientation of lines in structural geology
\citep{clark1986, allmendinger2012}.

PAREI AQUI

@@

Figure \ref{fig:figxxx} TEXT TEXT TEXT Fig. \ref{fig:figxxx} TEXT TEXT TEXT (Fig. \ref{fig:figxxx})

@@

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/structural_orientation_angles.png}
\caption{Schematic representation of the coordinate systems used to
represent an ellipsoidal body. 
(a) Main coordinate system with axes $x$, $y$, and $z$.
The dark gray plane contains the center $(x_{c}, y_{c}, z_{c})$
(white circle) and two unit vectors, $\mathbf{u}$ and $\mathbf{w}$, defining two
semi-axes of the ellipsoidal body. For triaxial and prolate ellipsoids,
$\mathbf{u}$ and $\mathbf{w}$ define, respectively, 
the semi-axes $a$ and $b$. For oblate ellipsoids, $\mathbf{u}$ and 
$\mathbf{w}$ define the semi-axes $b$ and $c$, respectively.
The strike direction is defined by the intersection of the
dark gray plane and the horizontal plane (represented in light gray),
which contains the $x$ and $y$ axes. The angle between "minus $x$"
and the strike direction is called \textit{strike}. The angle
between the horizontal plane and the dark gray plane
is called \textit{dip}. The line containing the unit vector
$\mathbf{u}$ defines the \textit{plunge direction}. The projection
of the plunge direction on the horizontal plane is called
\textit{plunge azimuth direction}. (b) Local coordinate system
with origin at the ellipsoid center $(x_{c}, y_{c}, z_{c})$
(black dot) and axes defined by unit vectors $\mathbf{v}_{1}$,
$\mathbf{v}_{2}$, and $\mathbf{v}_{3}$. These unit vectors
define the semi-axes $a$, $b$, and $c$ of triaxial, prolate,
and oblate ellipsoids. Notice that, for triaxial and prolate ellipsoids,
the unit vectors $\mathbf{u}$ and $\mathbf{w}$ shown in (a) coincide
with $\mathbf{v}_{1}$ and $\mathbf{v}_{2}$, respectively. For 
oblate ellipsoids, the unit vectors $\mathbf{u}$ and $\mathbf{w}$ 
shown in (a) coincide with $\mathbf{v}_{2}$ and $\mathbf{v}_{3}$,
respectively.}
\label{fig:orientation-angles}
\end{figure}

\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/demag_factors.pdf}
\caption{TEXT}
\label{fig:figxxx}
\end{figure}
